\textbf{(Positive Definite Matrices.)}  A \textit{principal submatrix}
$A_I$ of  an $n \times n$ matrix $A$ is obtained by picking a set $I
\subset \{1,2,\dots,n\}$ and crossing out all rows and columns whose
indices are not in $I$. For example, if \[
A = \left[
  \begin{matrix}
    a_{11} & a_{12} & a_{13} & a_{14} \\
    a_{21} & a_{22} & a_{23} & a_{24}\\
    a_{31} & a_{32} & a_{33} & a_{34}\\
    a_{41} & a_{42} & a_{43} & a_{44}
\end{matrix}
\right]
\]
then the principal submatrix corresponding to the set $\{2,4\}$ is \[
A_{\{2,4\}} = \left[
  \begin{matrix}
  a_{22} & a_{24} \\
  a_{42} & a_{44} \\
  \end{matrix}
\right]
\]
Show that every principal submatrix of a positive definite matrix is
positive definite.

{\color{blue}

For any positive definite matrix we can rearrange a column and a row
in the same way and preserve the properties positive definiteness and
symmetry. So without loss of generality we can consider just the
leading principal submatrices, rather than all possible permutations,
i.e. We can just look at $A_{\{1\}}, A_{\{1,2\}}, A_{\{1,2,\dots\}}, \dots$.

By induction, for the case $n=1$ our the only principal submatrix
$A_{\{1\}}$ is the same as $A$ and is trivial. For $n=2$ the only
principal submatrix will be $A_{\{1\}}$, and since $A_{\{1\}}$ is a
one dimension diagonal matrix we know that it's eigenvalue is the
element itself, which is positive, since the diagonals of $A$ are
positive, thus for $n=2$ this is still true.

Now assuming we have a positive definite matrix $A$ of size $n \times n$
and that all principle submatrices $A_{\{1\}}, A_{\{1,2\}}, \dots, A_{\{1,2,\dots,n-2\}}$ have been
proven to be positive definite, we have to show that
$A_{\{1,\dots,n-2\}}$ is also positive definite.

We know that the eigenvalues of $A_{\{1\}}, A_{\{1,2\}}, \dots, A_{\{1,2,\dots,n-2\}}$
are all positive, if we assume that the matrix $A_{\{1,2,\dots,n-1\}}$
is not positive definite, then it must have a non-positive eigenvalue.
However if this were the case then the matrix $A$ would also have to
contain a non-positive eigenvalue and we would have a contradiction.
Therefore $A_{\{1,2,\dots,n-1\}}$ must also be positive definite.

}
